Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Fix number missing

At the beginning of this research we paper, we defined a research question to be answered. This question was:
\emph{Does the visualization of emotions of young people (aged 16-26) by facial expression recognition software,
lead to discussion regarding the displayed content?}. In order to answer this question, we first defined how
we were going to capture emotions using technology. Once we reduced the scope to facial expression recognition,
we could continue with deciding how to visualize these captured emotions. We defined the emotions to
\emph{sadness, anger, contempt, disgust, fear, happiness, neutral, and surprise}, and chose a doughnut chart
as model for the visualization, based on prior research by the Waag Society. We then created a prototype
using open source tools and libraries, capable of predicting emotions from video and visualizing them according
to the aforementioned model.
Finally, we used the created prototype to conduct our user research. We tested the prototype with 13 different
subjects while interviewing them. The subsequent data analysis concluded that the prototype works largely as
expected. Our expectations and the results from the prototype were mostly correct, and X out of the 13 subjects
agreed with the emotions recognized by the prototype. The user research and data analysis also showed us the
imperfections of the prototype. This includes a number of unexpected emotions measured by the prototype.
This could be explained by too small of a dataset used to train the machine learning model responsible for
predicting the emotions. This is, however, something that would have to be researched in more detail in further
research.
We recommend further studies to focus on improving the visualization according to the feedback given to us by
our research subjects. Furthermore, increasing the dataset for the machine learning, and performing the user
research on a larger group of subjects. Additionally, the stability and speed of the prototype could also be
significantly improved, perhaps by switching over from Python to C++, and processing the video while it is still
being recorded.

>>>>

At the beginning of this research we paper, we defined a research question to be answered. This question was:
\emph{Does the visualization of emotions of young people (aged 16-26) by facial expression recognition software,
lead to discussion regarding the displayed content?}. In order to answer this question, we first defined how
we were going to capture emotions using technology. Once we reduced the scope to facial expression recognition,
we could continue with deciding how to visualize these captured emotions. We defined the emotions to
\emph{sadness, anger, contempt, disgust, fear, happiness, neutral, and surprise}, and chose a doughnut chart
as model for the visualization, based on prior research by the Waag Society. We then created a prototype
using open source tools and libraries, capable of predicting emotions from video and visualizing them according
to the aforementioned model.
Finally, we used the created prototype to conduct our user research. We tested the prototype with 13 different
subjects while interviewing them. The subsequent data analysis concluded that the prototype works largely as
expected. Our expectations and the results from the prototype were mostly correct, and 12 out of the 13 subjects
agreed with the emotions recognized by the prototype. The user research and data analysis also showed us the
imperfections of the prototype. This includes a number of unexpected emotions measured by the prototype.
This could be explained by too small of a dataset used to train the machine learning model responsible for
predicting the emotions. This is, however, something that would have to be researched in more detail in further
research.
We recommend further studies to focus on improving the visualization according to the feedback given to us by
our research subjects. Furthermore, increasing the dataset for the machine learning, and performing the user
research on a larger group of subjects. Additionally, the stability and speed of the prototype could also be
significantly improved, perhaps by switching over from Python to C++, and processing the video while it is still
being recorded.
